### 2018-09-30 revfiles/internalComments.rmd

Rewording was also great.

@@

Thanks for the feedback. I'll also try to make it sound less dodgy.

@@

I agree that it should be self evident but this is something that some of my colleagues, who are not familiar with phages, appreciated hearing.

>>>>

Rewording was also great, thanks.

@@

Thanks for the feedback. I also tried to make it sound less dodgy.

@@

I agree that it should be self evident but this is something that some of my colleagues, who are not familiar with phages (e.g. clinicians), have appreciated hearing.
